---
title: "QAQC Comparison Report"
format: html
execute:
  echo: true
---

## QAQC

```{r setup}
library(targets)
library(data.table)
library(ggplot2)
source("qaqc/comparison_functions.R")
tar_load(qaqc_summary)
```

### Climate data preparation

First steps involve preparing climate data to derive a moisture index. (Step 1) Shift calendar year months to better align with growth period. Northern hemisphere 1971 year starts in September 1970 and ends in August of 1971 Southern hemisphere 1971 year starts in March 1971 and ends in Februrary 1972 (Step 2) Calculate monthly: a. Potential Evapotranpiration (PET), b. Water Balance (BAL), and c. Standardized Preciptation-Evapotranspiration Index (SPEI) (Step 3) Aggregate monthly climate to yearly to match tree ring temporal resolution.

```{r}
res1 <- plot_compare(qaqc_summary$climate_prep$step1)
res1$stats

res1$plots

res2 <- plot_compare(qaqc_summary$climate_prep$step2)
res2$stats

res2$plots

res3 <- plot_compare(qaqc_summary$climate_prep$step3)
res3$stats

res3$plots

```

### Merge climate and growth

Climate and Growth Ring data are then merged together.

```{r}
res_merge <- plot_compare(qaqc_summary$merge$comp_clim_grw_merge)
res_merge$stats

res_merge$plots

```

### Flag drought ***events***

Drought events are calculated for each individual Id (Site).

```{r}
res_flags <- plot_compare(qaqc_summary$drought_flags)
res_flags$stats

res_flags$plots

```

### Flag drought ***years***

Drought events are summarized into common drought years for the region.

```{r}
res_years <- plot_compare(qaqc_summary$drought_years)
res_years$stats

res_years$plots

```

### Expand dataset

Dataset is expanded to make sure every drought year of every site can have growth data aggregated into average pre-drought growth (2 years) and average pos-drought growth (2 years)

```{r}
```

### Calculate RRR

Resistance, Recovery and Resilience indices are calculated based on drought years for each site.

```{r}
```

### Model RRR

Resilience is modeled using negative exponential function.

```{r}
```

### Calculate RED50

Resilience at 50% resistance (RED50) is predicted for each site

```{r}
```

### Summarise RED50

RED50 is aggregated to group level.

```{r}
```
